

---
title: Results of Supra-National Inter-Laboratory Comparison of Samples from Suspected
  TB Cases
author: 'Laboratory under evaluation: CERMEL'
date: '`r Sys.Date()`'
output:
  pdf_document:
    includes:
      in_header: logoCermel.tex
    keep_tex: yes
  word_document:
    fig_caption: yes
    fig_height: 3
    fig_width: 7
logo: null
---

**Supra-National Laboratory**: German National Reference Center for Tuberculosis, Borstel

Method:
======
Ziehl-Neelsen Smear
```{r data1,echo=FALSE,message=FALSE,cache=TRUE}
##Importing and manipulation data
library(xlsx) 
data0 <- read.xlsx(NameTable, 1, header=T)
data2 <- data0[,c(1:12)]
data3 <- data2
levels(data3$ZN_CERMEL)<-c(rep(1,4),rep(0,2))
levels(data3$ZN_Borstel)<-c(rep(1,5),rep(0,2))
```

Dates
=====
```{r dat,  echo=FALSE, message=FALSE}
#Convert to date
data3$Date_Specimen <-as.Date(strptime(data3$Date_Specimen, format="%Y-%m-%d"))
```
**`r min(data3$Date_Specimen)`** to **`r max(data3$Date_Specimen)`**

Sample frame 
============
- Total sample: `r nrow(data3)`
- CERMEL positives: `r table(data3$ZN_CERMEL)[1]`/`r table(data3$ZN_CERMEL)[1]`
- CERMEL negatives: `r table(data3$ZN_CERMEL)[2]`/`r table(data3$ZN_CERMEL)[2]`

Summary table
=============
```{r tab1, results='asis',echo=F,message=FALSE}
##Crosstable
tab1 <- table(data3$ZN_CERMEL, data3$ZN_Borstel)
dimnames(tab1) <- list(CERMEL = c('Positive','Negative'), Borstel =c('Positive', 'Negative'))
library(knitr)
tab1 <- as.data.frame(tab1)
names(tab1)[3] <-"N"
kable(tab1)
```

\pagebreak

Discordant table
================
```{r tab2, results='asis',echo=FALSE, message=FALSE}
##Searching ID_CERMEL discordant
disc_index <- which(data3$ZN_CERMEL!=data3$ZN_Borstel)
disc_NameCode <- data3$ID_CERMEL[disc_index]

##Discordant Table 
tab2 <- subset(data0, is.element(data0[,2],disc_NameCode))
tab2 <- tab2[,1:12]
kable(tab2[,c(2,4,9,10,11,12)],row.names = F)
```

Accuracy, overall
================
```{r tab3, echo=FALSE, results='asis',message=FALSE}
tab3 <- table(data3$ZN_CERMEL, data3$ZN_Borstel)
cord1 <- sum(tab3[1,1]+tab3[2,2])
tot1 <- sum(tab3)
cord2 <- tot1-cord1
nPCERMEL <- sum(tab3[1,1]+tab3[1,2])
nNCERMEL <- sum(tab3[2,1]+tab3[2,2])
```

- Concordant sample N(%): `r cord1` (`r round(100*cord1/tot1,0)`%)
- Discordant sample N(%): `r cord2` (`r round(100*cord2/tot1,0)`%)
    + False positives N(%): `r tab3[1,2]` (`r round(100*tab3[1,2]/nPCERMEL,0)`%)
    + False negatives N(%): `r tab3[1,2]` (`r round(100*tab3[2,1]/nNCERMEL,0)`%)

```{r tab3b, echo=FALSE, results='asis',message=FALSE}

##Data manipulation
library(chron)
data3$quarter <- quarters(as.chron(data3$Date_Specimen))
levels(data3$quarter) <-c('Jan-Mar', 'Apr-Jun', 'Jul-Sep', 'Oct-Dec')
data_oct_dec <- subset(data3, quarter=='Oct-Dec')

tab_oct_dec <- table(data_oct_dec$ZN_CERMEL, data_oct_dec$ZN_Borstel)
cord1 <- sum(tab_oct_dec[1,1]+tab_oct_dec[2,2])
tot1 <- sum(tab_oct_dec)
cord2 <- tot1-cord1
nPCERMEL <- sum(tab_oct_dec[1,1]+tab_oct_dec[1,2])
nNCERMEL <- sum(tab_oct_dec[2,1]+tab_oct_dec[2,2])
```

Accuracy, most recent quarter (Oct-Dec)
=======================================
- Total sample: `r nrow(data_oct_dec)`
- Concordant sample N(%): `r cord1` (`r round(100*cord1/tot1,0)`%)
- Discordant sample N(%): `r cord2` (`r round(100*cord2/tot1,0)`%)
    - False positives N(%): `r tab_oct_dec[1,2]` (`r round(100*tab_oct_dec[1,2]/nPCERMEL,0)`%)
    - False negatives N(%): `r tab_oct_dec[1,2]` (`r round(100*tab_oct_dec[2,1]/nNCERMEL,0)`%)



Tagret accuracy: Percentage discordant samples (5%)
====================================================
```{r fig1,  echo=FALSE, message=FALSE, fig.show='asis'}
library(ggplot2)
tab2$Date_Specimen <-as.POSIXlt(strptime(tab2$Date_Specimen, format="%Y-%m-%d"))
tab2$quater <- quarters(as.chron(tab2$Date_Specimen))
levels(tab2$quater) <-c('Jan-Mar', 'Apr-Jun', 'Jul-Sep', 'Oct-Dec')

#graphic
tab4 <-table(tab2$quater)
tab4 <-as.data.frame(tab4)
tab2a <- subset(data0, !is.element(data0[,2],disc_NameCode))

tab2a$Date_Specimen <-as.POSIXlt(strptime(tab2a$Date_Specimen, format="%Y-%m-%d"))
tab2a$quater_a <- quarters(as.chron(tab2a$Date_Specimen))
levels(tab2a$quater_a) <-c('Jan-Mar', 'Apr-Jun', 'Jul-Sep', 'Oct-Dec')
tab4a <-table(tab2a$quater_a)
tab4a <-as.data.frame(tab4a)

tab5 <-cbind(tab4, tab4a$Freq)
tab5 <- transform(tab5, per=100*Freq/(tab4a$Freq+Freq))
tab6 <-rbind(tab4, tab4a)
tab6$Disc <-as.factor(c(rep("Discordant",4), rep("Concordant",4)))
#########################################################################

##Plot discordant lines
fig1 <-ggplot(tab5, aes(x=Var1, y=per,ymin=0, group=4)) + geom_line() + geom_point()+
  xlab('Time')+ylab('Discordants (%)')+
  geom_hline(yintercept = 5, colour="red", linetype = "longdash")+
  annotate("text", x=0.8, y=5.5, label="Tagret accuracy", colour="red", size=3)
fig1

##Plot barplot discordant
fig2 <-ggplot(tab6, aes(x=Var1, y=Freq, ymax=max(Freq)+5, fill=Disc)) +
geom_bar(stat="identity", position="dodge") +
geom_text(aes(label=Freq), vjust=-0.5, colour="black",
position=position_dodge(.9), size=4)+xlab('Time')+ylab('Count (n)')+
guides(fill=guide_legend(title=NULL))+scale_fill_manual(values = c("grey","black"))+
theme(legend.position="top") 
fig2
#########################################################################
```











